Hadoop Image Processing Framework

### 2015-03-12 Paper.tex
Rewritten introduction

	\section{Introduction}
	With the spread of social media in recent years a large amount of image data is accumulated. Processing this large image data is limited to single computer which lack in computational power and storage ability. These tasks typically be performed on a distributed system by dividing the task into sever sub tasks. The ability to parallelize tasks allows for scalable, efficient, execution of resource-intensive applications. Hadoop MapReduce framework provides a platform for such tasks.

	Also, when considering operations such as face detection, image classification\cite{Li2009} and other types of processing on images, there are limits on what can be done to improve performance of single computers to make them able to process large-scale information. Therefore, the advantages of parallel distributed processing of a large image dataset by using the computational resources of cloud computing environment can be considered. In addition, if computational resources can be secured easily and relatively inexpensively, then cloud computing in suitable for handling large size image data sets at very low cost and increased performance. Hadoop, as a system for processing large numbers of images by parallel and distributed computing seems promising. In fact, Hadoop is in use all over the world. Studies using Hadoop have been performed to treat one file as a text data file or multiple files as a single file unit, such as for the analysis of large volumes of DNA sequence data, converting the data of a large number of still images to PDF format, and carrying out feature selection/extraction in astronomy. These examples demonstrate the usefulness of this system, which is due to its having the ability to run multiple processes in parallel for load balancing and task management.

	Most of the image processing applications, that use Hadoop MapReduce framework require a staggering learning curve and high complexity. The overhead required to implement such applications is cumbersome to users. Hadoop Image Processing Framework hides the highly technical deatails of Hadoop system and provides users with a feel of an normal image processing library giving the users the access to advanced resources of distributed system. Our framework mainly focuses around giving users an easy way to access the image data allowing for easy and flexible use for large scale image applications

	Hadoop Image Processing Framework is largely a software design project, with a goal of hiding Hadoop's functionality and provide users with a library to effectively use Hadoops MapReduce system for large scale image processing. We believe that the ease of use and java oriented semantics will make the process of creating large scale image experiments further more easier. This framework is an excellent tool for Hadoop novice users and image processing researchers because it allows development of large scale image processing applications.

	In the following section  we will describe prior work in this area. Next we describe the overview for the Hadoop Image Processing Framework including the Downloader, Processor and Extractor statges. Additionally, we describe our approach of distributing tasks for MapReduce. Finally we demonstrate the potential of this framework with a few examples of image processing.

	\section{Prior Work}
	With rapid increase of usage of online photo storage and social media like facebook, flickr and picasa the amount of image data available is larger than ever before. The amount of image data is growing rapidly every day. According to Buzzfeed for every minute 27800 photos are uploaded to Instagram. As per facebook, they get 208,300 photos uploaded every minute\cite{Horaczek2013}. This alone provides a plethora of image that can scale up to billions of images. It is these reasons that motivate the need for research with image processing applications that take advantage of large sets of images

>>>>

	\section{Introduction}
	With the spread of social media in recent years, a large amount of image data has been accumulating. When processing this massive data resource has been limited to single computers, computational power and storage ability quickly become bottlenecks. Alternately, processing tasks can typically be performed on a distributed system by dividing the task into several subtasks. The ability to parallelize tasks allows for scalable, efficient execution of resource-intensive applications.  The Hadoop MapReduce framework provides a platform for such tasks.

	When considering operations such as face detection, image classification\cite{Li2009} and other types of processing on images, there are limits on what can be done to improve performance of single computers to make them able to process information at the scale of social media. Therefore, the advantages of parallel distributed processing of a large image dataset by using the computational resources of a cloud computing environment should be considered. In addition, if computational resources can be secured easily and relatively inexpensively, then cloud computing is suitable for handling large image data sets at very low cost and increased performance. Hadoop, as a system for processing large numbers of images by parallel and distributed computing, seems promising. In fact, Hadoop is in use all over the world. Studies using Hadoop have been performed, dealing with text data files, analyzing large volumes of DNA sequence data, converting the data of a large number of still images to PDF format, and carrying out feature selection/extraction in astronomy. %Cite the papers in which these examples appear
These examples demonstrate the usefulness of the Hadoop system, which can run multiple processes in parallel for load balancing and task management.

	Most of the image processing applications that use the Hadoop MapReduce framework are highly complex and impose a staggering learning curve.  The overhead, in programmer time and expertise, required to implement such applications is cumbersome.  To address this, we present the Hadoop Image Processing Framework, which hides the highly technical details of the Hadoop system and allows programmers who can implement image processing algorithms but who have no particular expertise in distributed systems to nevertheless leverage the advanced resources of a distributed, cloud-oriented Hadoop system. Our framework provides users with easy access to large-scale image data, smoothly enabling rapid prototyping and flexible application of complex image processing algorithms to very large, distributed image databases.

	The Hadoop Image Processing Framework is largely a software engineering platform, with the goal of hiding Hadoop's complexity while providing users with the ability to use the system for large-scale image processing without becoming crack Hadoop engineers.  The framework's ease of use and Java-oriented semantics will further ease the process of creating large scale image applications and experiments. This framework is an excellent tool for novice Hadoop users, image application developers and computer vision researchers, allowing the rapid development of image software that can take advantage of the huge data stores, rich metadata and global reach of current online image sources.

	In the following section  we will describe prior work in this area. Next we present an overview of the Hadoop Image Processing Framework including the Downloader, Processor and Extractor stages. Additionally, we describe our approach of distributing tasks for MapReduce. Finally, we demonstrate the potential of this framework with quantitative analysis and experiments performed on image processing tasks.

	\section{Related Work}
	With rapid increase of usage of online photo storage and social media like facebook, flickr and picasa the amount of image data available is larger than ever before. The amount of image data is growing rapidly every day. According to Buzzfeed for every minute 27800 photos are uploaded to Instagram. As per facebook, they get 208,300 photos uploaded every minute\cite{Horaczek2013}. This alone provides a plethora of image that can scale up to billions of images. It is these reasons that motivate the need for research with image processing applications that take advantage of large sets of images
